\documentclass[11pt,a4paper]{article}

\usepackage[a4paper, top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setlist[itemize]{leftmargin=1.2em, label=--, topsep=0pt, itemsep=0.05em}
\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Simon-Hans Edasi}} \\[6pt]
    simonhansedasi@gmail.com \hfill \textbar \hfill
    simonhansedasi.github.io \hfill \textbar \hfill
    linkedin.com/in/simon-hans-edasi
\end{center}

\section*{Summary}
Integration-focused technologist with 5+ years bridging operational workflows and technical systems
in financial and data-intensive environments. Experienced in analyzing manual processes, designing
automation solutions, and coordinating implementation across functional and technical teams. Builds
repeatable, well-documented data pipelines and integration architectures with an emphasis on
governance, auditability, and operational reliability.

\section*{Skills}
\begin{itemize}
  \item \textbf{Integration \& Automation:} ERP integration (Microsoft Great Plains, SmartConnect),
        workflow analysis, process automation, data transformation pipelines, ETL design
  \item \textbf{Data \& Reporting:} Excel (advanced), Python, SQL, SQLite, pandas, data modeling,
        financial data prep, repeatable reporting workflows
  \item \textbf{Architecture \& Governance:} API design, system integration testing, audit logging,
        policy enforcement, cost governance, multi-system data routing, documentation
  \item \textbf{Infrastructure \& Ops:} Flask, nginx, Gunicorn, systemd, Raspberry Pi, DigitalOcean,
        Tailscale VPN, Linux, shell scripting
  \item \textbf{Platforms \& APIs:} Anthropic API, OpenAI API, Twilio, USAJOBS, RapidAPI, Census API,
        Google Earth Engine, Google Calendar API
\end{itemize}

\section*{Work Experience}

\textbf{AR Specialist} \hfill \textit{RANDY's} \hfill 2025
\begin{itemize}
  \item Served as functional architect for ERP integration workflows -- analyzed manual AR processes,
        identified automation opportunities, and designed solutions implemented via SmartConnect
        and Microsoft Great Plains.
  \item Led user acceptance testing for integration builds; diagnosed data flow failures and
        coordinated fixes between business operations and the ERP implementation specialist.
  \item Digitized records management workflows, eliminating paper-based processes and establishing
        repeatable, auditable data handling procedures.
  \item Authored shell scripts to automate file organization and records maintenance, reducing
        recurring manual effort across the AR team.
  \item Prepared and transformed financial data in Excel for reporting and reconciliation workflows,
        ensuring accuracy and consistency across billing cycles.
\end{itemize}

\vspace{0.4em}
\textbf{NCO} \hfill \textit{U.S. Air Force} \hfill 2008--2014
\begin{itemize}
  \item Led mandatory training for unit personnel under sensitive, high-stakes conditions across
        mixed ranks and diverse audiences; developed facilitation and structured communication skills
        applicable to cross-functional technical collaboration.
\end{itemize}

\section*{Selected Projects}

\textbf{ai\_glue -- LLM Audit \& Governance Layer} \hfill \textit{Python, Flask, SQLite}
\begin{itemize}
  \item Built a drop-in observability and governance proxy for Anthropic and OpenAI APIs; logs every
        AI call with token counts, cost, latency, and project labels across 3 deployed instances.
  \item Implements live-reloadable governance rules: model allowlists, cost caps, rate limits, PII
        detection, and per-team API key routing -- zero restart required on rule changes.
  \item Parent-child multi-instance aggregation enables org-wide cost visibility; JSONL export
        supports fine-tuning pipelines; 27-test mock suite requires no live API keys.
\end{itemize}

\vspace{0.3em}
\textbf{RippleForge -- Production SaaS (rippleforge.gg)} \hfill \textit{Python, Flask, SQLite, nginx}
\begin{itemize}
  \item Multi-tenant web application with live paying users; deployed on DigitalOcean behind nginx
        and Gunicorn with Let's Encrypt SSL; full audit trail via ai\_glue integration.
  \item Two-step deploy pipeline (pytest suite + rsync + deploy script) enforces test coverage
        before every production push; operational runbooks maintained for all integrations.
\end{itemize}

\vspace{0.3em}
\textbf{rejection\_matrix -- Integration Pipeline \& Tracker} \hfill \textit{Python, Flask, SQLite}
\begin{itemize}
  \item Aggregates job listings across 5 board APIs (Remotive, WWR, JSearch, USAJOBS, Ashby) with
        board-specific query logic, salary normalization, and deduplication.
  \item Append-only audit log per record; SSE-streaming Flask UI; daily cron pipeline with ntfy.sh
        alerting -- demonstrates full integration lifecycle from ingestion to governance.
\end{itemize}

\vspace{0.3em}
\textbf{snotrac -- Transit Accessibility \& Equity Analysis} \hfill \textit{Python, geopandas, pandas}
\begin{itemize}
  \item Fused GTFS transit feeds, ACS demographic layers, and OSM road networks into a
        frequency-weighted accessibility model covering all of Snohomish County.
  \item Designed a composite Gap Score (vulnerability index x inverse log-accessibility) to
        surface underserved populations; outputs delivered as interactive maps and a policy
        brief to regional agencies.
  \item Multi-source pipeline with automated data acquisition (Census API, GTFS auto-download,
        OSM via osmnx); fully documented and reproducible from raw inputs to final report.
\end{itemize}

\section*{Education}
\textbf{B.S. Geophysics} -- University of Washington \hfill \textit{2023} \\
\textbf{A.S. Physics} -- Edmonds College \hfill \textit{2020}

\section*{Publications}
Edasi, S.-H. et al. (2026). \textit{Global glacier thickness estimates from a shallow neural network.}
Journal of Glaciology 72, e28, 1--8. DOI: 10.1017/jog.2026.10123

\end{document}
