\documentclass[11pt,a4paper]{article}

\usepackage[a4paper, top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setlist[itemize]{leftmargin=1.2em, label=--, topsep=0pt, itemsep=0.05em}
\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Simon-Hans Edasi}} \\[6pt]
    simonhansedasi@gmail.com \hfill \textbar \hfill
    simonhansedasi.github.io \hfill \textbar \hfill
    linkedin.com/in/simon-hans-edasi
\end{center}

\section*{Summary}
Integration-focused technologist with 5+ years bridging operational workflows and technical systems
in financial and data-intensive environments. Experienced in analyzing manual processes, designing
automation solutions, and coordinating implementation across functional and technical teams. Builds
repeatable, well-documented data pipelines and integration architectures with an emphasis on
governance, auditability, and operational reliability.

\section*{Skills}
\begin{itemize}
  \item \textbf{Integration \& Automation:} ERP integration (Microsoft Great Plains, SmartConnect),
        workflow analysis, process automation, data transformation pipelines, ETL design
  \item \textbf{Data \& Reporting:} Excel (advanced), Python, SQL, SQLite, pandas, data modeling,
        financial data prep, repeatable reporting workflows
  \item \textbf{Architecture \& Governance:} API design, system integration testing, audit logging,
        policy enforcement, cost governance, multi-system data routing, documentation
  \item \textbf{Middleware \& Integration Tools:} SmartConnect, REST API integration, multi-system
        data routing, webhook design, ETL pipeline architecture
\end{itemize}

\section*{Work Experience}

\textbf{AR Specialist} \hfill \textit{RANDY's} \hfill 2025
\begin{itemize}
  \item Served as functional architect for ERP integration workflows -- analyzed manual AR processes,
        identified automation opportunities, and designed solutions implemented via SmartConnect
        and Microsoft Great Plains.
  \item Led user acceptance testing for integration builds; diagnosed data flow failures and
        coordinated fixes between business operations and the ERP implementation specialist.
  \item Digitized records management workflows, eliminating paper-based processes and establishing
        repeatable, auditable data handling procedures.
  \item Authored shell scripts to automate file organization and records maintenance, reducing
        recurring manual effort across the AR team.
  \item Prepared and transformed financial data in Excel for reporting and reconciliation workflows,
        ensuring accuracy and consistency across billing cycles.
\end{itemize}

\vspace{0.4em}
\textbf{Administrative Specialist} \hfill \textit{UW Earth \& Space Sciences} \hfill 2017--2022
\begin{itemize}
  \item Reconciled ~150 transactions per week across purchase orders, reimbursements, travel,
        and grants; verified account coding, tax treatment, and documentation completeness
        across My Financial Desktop, Workday, and Ariba.
  \item Built a color-coded Excel reconciliation tracker using conditional formatting to display
        at-a-glance budget status across all department accounts; automated recurring receipt
        collection via scheduled email, eliminating manual retrieval of interdepartmental
        compute charges each billing cycle.
  \item Maintained departmental financial records; fulfilled audit records requests with full
        chain-of-custody documentation.
\end{itemize}


\section*{Selected Projects}

\textbf{ai\_glue -- API Governance \& Audit Layer} \hfill \textit{Python, Flask, SQLite}
\begin{itemize}
  \item Designed and deployed a policy enforcement layer governing API access across
        3 production instances; rules cover allowlists, cost caps, rate limits, and
        PII detection -- all live-reloadable without service interruption.
  \item Append-only audit log captures every integration event with cost, latency,
        and project attribution; enables full traceability and cost accountability
        across teams.
  \item Automated PII detection flags sensitive data in transit before it reaches
        external endpoints; enforces data handling policies without manual intervention.
\end{itemize}



\section*{Education}
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r@{}}
  \textbf{Certificate, Data Science} & University of Washington & \textit{2025} \\
  \textbf{M.S. Earth \& Space Sciences} & University of Washington & \textit{2024} \\
  \textbf{B.S. Earth \& Space Sciences} & University of Washington & \textit{2019} \\
\end{tabular*}


\end{document}
