\documentclass[11pt,a4paper]{article}

\usepackage[a4paper, top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setlist[itemize]{leftmargin=1.2em, label=--, topsep=0pt, itemsep=0.05em}
\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Simon-Hans Edasi}} \\[6pt]
    simonhansedasi@gmail.com \hfill \textbar \hfill
    simonhansedasi.github.io \hfill \textbar \hfill
    linkedin.com/in/simon-hans-edasi
\end{center}

\vspace{0.3cm}

\noindent
\textbf{Aerospace maintenance professional with 6 years of USAF flightline experience inspecting and maintaining mission-critical avionics systems. Trained to zero-defect standards under military aerospace regulatory compliance. Proficient in Technical Order interpretation, precision measurement, FOD prevention, and confined-space and elevated-work environments. Holds a graduate degree and published research in data-driven analysis; brings systematic, documentation-rigorous approach to quality inspection work.}

% =========================
\section*{Experience}

\noindent
\textbf{Flightline Maintenance Craftsman} \hfill US Air Force \hfill 2008--2014
\begin{itemize}
    \item Performed pre-flight, thru-flight, and post-flight inspections of aircraft avionics systems; documented all discrepancies and corrective actions in maintenance management systems under zero-tolerance accuracy requirements.
    \item Interpreted and executed maintenance and inspection procedures from Air Force Technical Orders --- the military equivalent of engineering drawings and specifications --- for complex avionics installations, alignments, and system verification checks.
    \item Used precision measurement tools and calibrated test equipment to verify system tolerances, clearances, and conformance to specification during inspection and installation tasks.
    \item Participated in daily FOD (Foreign Object Debris) prevention walks and enforced strict FOD awareness protocols on the flight line to protect aircraft from foreign object damage.
    \item Performed maintenance in confined spaces and at elevated heights on aircraft; complied with fall protection procedures and respiratory protection requirements for fuel system and chemical exposure environments.
    \item Managed cryptographic security program controlling access to encrypted communication systems; maintained audit-ready documentation under DoD compliance standards.
\end{itemize}

\vspace{0.2cm}
\noindent
\textbf{Accounts Receivable Specialist (Contract)} \hfill Randy's World-Wide \hfill Mar--Aug 2025
\begin{itemize}
    \item Reconciled hundreds to thousands of invoice and payment transactions weekly from Microsoft Great Plains ERP; identified discrepancies and documented findings with audit-ready accuracy.
    \item Built Python automation tools to process and validate transaction data; designed rule-based anomaly detection to flag mismatched records.
\end{itemize}

\vspace{0.2cm}
\noindent
\textbf{Administrative Aide (Finance \& Operations)} \hfill University of Washington \hfill 2017--2022
\begin{itemize}
    \item Maintained financial and administrative records supporting compliance and audit readiness.
\end{itemize}

\vspace{0.2cm}
\noindent
\textbf{Independent Research} \hfill 2025--Present
\begin{itemize}
    \item Published first-author research in \textit{Journal of Glaciology} (2026); trained a neural network on 216,501 glacier surface attributes with rigorous cross-validation and uncertainty quantification.
    \item Designed and deployed a production data collection platform (Flask, SQLite) with systematic data validation and quality control workflows.
\end{itemize}

% =========================
\section*{Education}

\noindent
\textbf{Data Science Certificate} \hfill University of Washington \hfill 2025

\vspace{0.1cm}
\noindent
\textbf{MSc., Geophysical Data Science} \hfill University of Washington \hfill GPA: 3.7 \hfill 2024

\vspace{0.1cm}
\noindent
\textbf{BSc., Earth \& Space Sciences} \hfill University of Washington \hfill GPA: 3.4 \hfill 2019

% =========================
\section*{Publications}

\noindent
\textbf{Edasi, SH., Lipovsky, B.P.} ``Tidewater and lake-terminating glaciers are systematically thicker.'' \textit{Journal of Glaciology} 72, e28, 1--8 (2026). \href{https://doi.org/10.1017/jog.2026.10123}{doi:10.1017/jog.2026.10123}

\end{document}
